% Chapter 6

\chapter{Introduction} % Main chapter title

\label{chapter:introduction}

The ever occurring question \emph{"Can quantum $x$ beat the classical variant?"} was once a synonym for \emph{theoretically, yes}. For a long time all possible gains remained in the theoretical realm\cite{shor_polynomial-time_1997}, but current advances in the field of quantum computing have brought out solutions and proposals\cite{farhi_quantum_2014, fankhauser_multiple_2021, havlicek_supervised_2019} that can be programmed and used \emph{today}. At the same time quantum computing is getting more and more available to non-researchers as IBM, Microsoft, Google and co. fight for dominance in this new field of computation.\par
The training of neural networks demands an ever increasing amount of computational power\cite{openai_ai_2018} to train algorithms that can solve the worlds hardest problems. The goal of this paper is to evaluate current quantum offerings to solve classification problems as well as analyse their performance. In a first step, the application of features and weights onto a quantum gates and their behaviour is assessed. Subsequently two possible designs are evaluated. The first solution replicates the basic arithmetic operations computational neurons use, and the second one uses quantum specific superpositions and entanglement. Due to the necessary amount of qubits for the arithmetic solution, as well as the absence of quantum specific operations, only the the classifier based on entanglement and superpositions is further developed and evaluated.\par 
Using a variety of different quantum circuits, as well as three different datasets, training is done on the simulator to determine the viability of these designs as well as to compare them to a basic \code{MLP} classifier. The results show that the right combination of quantum gates leads to a more flexible classifier, that can adapt and solve different problem spaces. One problem that accompanies these design is the disparity when it comes to achieved accuracy. Under reproducible circumstances, no two training results are equal. This problem comes directly from the vast expressability such a circuit offers - by making the problem space much wider, it gets harder to traverse and therefor, find a viable solution.\par 
When running the trained circuit on real hardware for a given dataset, another problem arises as the noise affecting a real devices disrupts the operations and leads to vastly inferior accuracy. As current The findings show that quantum circuits can offer a substantial gain when compared to the classical solutions, but still need more refinement before being touted as a viable alternative, without regards to hardware availability. 